Optimal (Multiway) Spatial Joins

### 2024-06-01 msj.tex
yufei

\extraspacing {\bf Proof of Lemma~\ref{lmm:hv:type1:properties}.}
\underline{\em Proof of Statement (1).} As $h \in \dcross_H(\bm{t})$ and $v \in \dcross_V(\bm{t})$, the two segments both cross $B_\bm{t}$, as can be verified from the definitions of $\dcross_H(\bm{t})$ and $\dcross_V(\bm{t})$. Thus, the intersection of $h$ and $v$ is a point $p$ in $B_\bm{t}$. As $r_i$ (for each $i \in [k-2]$) is the full rectangle of $\bm{t}[i]$, we know that $\bigcap_{i=1}^{k-2} r_i$ covers $B_\bm{t} = \bigcap_{i=1}^{k-2} \bm{t}[i]$. Hence, point $p$ falls in $\bigcap_{i=1}^{k-2} r_i$, indicating that $h\cap v \cap \bigcap_{i = 1}^{k-2}r_i \neq \emptyset$. It follows that $(r_1,...,r_{k-2},h,v)$ is a result tuple in $\J(R_1,...,R_{k-2},H,V)$.

\noindent \underline{\em Proof of Statement (2).} Fix any rectangle $r \in R_1 \cup ... \cup R_{k-2}$ and any horizontal segment $h = [x_1, x_2] \times y$ from $H$ that crosses $r$. We will show that $h$ must also cross the trimmed rectangle $r'$ of $r$. From the fact of $h$ crossing $r$, it is clear that $[x_1, x_2]$ contains the x-range of $r$. As the x-range of $r$ contains that of $r'$, we can assert that $[x_1, x_2]$ contains the x-range of $r'$. To prove that $h$ crosses $r'$, we still need to show $y \in [\ybot(r'), \ytop(r')]$. Recall that $\ybot(r')$ is the y-coordinate of the lowest segment in $H$ crossing $r$. This implies $y \ge \ybot(r')$ because $h$ itself is a segment in $H$ crossing $r$. Analogously, it also holds that $y \le \ytop(r')$. We can thus conclude that $h$ crosses $r'$.

@@

\noindent \underline{\em Proof of Statement (3).} We first prove that $\dcross_H(\bm{t}) \neq \emptyset$ for any $\bm{t} \in \J(R_1',...,R_{k-2}')$. Set $r' = \gbot(\bm{t})$, and let $r$ be the full rectangle of $r'$. Define $h$ as the lowest segment crossing $r$ (note that $h$ definitely exists because otherwise $r$ has no trimmed rectangle). We will show that $h \in \dcross_H(\bm{t})$, and hence $\dcross_H(\bm{t})$ cannot be empty. For this purpose, we should explain why $h$ crosses both $B_{\bm{t}}$ and $r'$. However, $h$ crossing $r$ implies $h$ crossing $r'$, as has already been argued in our proof of statement (2). It remains to show that $h$ crosses $B_\bm{t}$.

@@

\extraspacing {\bf Proof of Lemma~\ref{lmm:hv:type1:cross-r*}.}
\underline{\em Proof of Statement (1).} We will map each $r^*$ of $\bigcup_{i = 1}^{k-2} R_i^*$ to a unique tuple $\bm{t}$ in $\J(R_1',...,R_{k-2}')$ satisfying $\dcross_H(\bm{t})$ $= \cross_H(r^*)$. After this, we can then derive
\myeqn{
    \sum_{i\in[k-2]}\sum_{r^*\in R_i^*} |\cross_H(r^*)| \leq \sum_{\bm{t}\in \J(R_1',...,R_{k-2}')}|\dcross_H(\bm{t})|\leq \out \nn
}
where the last step used  statement (3) of Lemma~\ref{lmm:hv:type1:properties}.

>>>>

\extraspacing {\bf Proof of Lemma~\ref{lmm:hv:type1:properties}.} We will prove each statement in turn.

\extraspacing \underline{\em Proof of Statement (1).} As $h \in \dcross_H(\bm{t})$ and $v \in \dcross_V(\bm{t})$, the two segments both cross $B_\bm{t}$, as can be verified from the definitions of $\dcross_H(\bm{t})$ and $\dcross_V(\bm{t})$. Thus, the intersection of $h$ and $v$ is a point $p$ in $B_\bm{t}$. As $r_i$ (for each $i \in [k-2]$) is the full rectangle of $\bm{t}[i]$, we know that $\bigcap_{i=1}^{k-2} r_i$ covers $B_\bm{t} = \bigcap_{i=1}^{k-2} \bm{t}[i]$. Hence, point $p$ falls in $\bigcap_{i=1}^{k-2} r_i$, indicating that $h\cap v \cap \bigcap_{i = 1}^{k-2}r_i \neq \emptyset$. It follows that $(r_1,...,r_{k-2},h,v)$ is a result tuple in $\J(R_1,...,R_{k-2},H,V)$.

\extraspacing \underline{\em Proof of Statement (2).} Fix any rectangle $r \in R_1 \cup ... \cup R_{k-2}$ and any horizontal segment $h = [x_1, x_2] \times y$ from $H$ that crosses $r$. We will show that $h$ must also cross the trimmed rectangle $r'$ of $r$. From the fact of $h$ crossing $r$, it is clear that $[x_1, x_2]$ contains the x-range of $r$. As the x-range of $r$ contains that of $r'$, we can assert that $[x_1, x_2]$ contains the x-range of $r'$. To prove that $h$ crosses $r'$, we still need to show $y \in [\ybot(r'), \ytop(r')]$. Recall that $\ybot(r')$ is the y-coordinate of the lowest segment in $H$ crossing $r$. This implies $y \ge \ybot(r')$ because $h$ itself is a segment in $H$ crossing $r$. Analogously, it also holds that $y \le \ytop(r')$. We can thus conclude that $h$ crosses $r'$.

@@

\extraspacing \underline{\em Proof of Statement (3).} We first prove that $\dcross_H(\bm{t}) \neq \emptyset$ for any $\bm{t} \in \J(R_1',...,R_{k-2}')$. Set $r' = \gbot(\bm{t})$, and let $r$ be the full rectangle of $r'$. Define $h$ as the lowest segment crossing $r$ (note that $h$ definitely exists because otherwise $r$ has no trimmed rectangle). We will show that $h \in \dcross_H(\bm{t})$, and hence $\dcross_H(\bm{t})$ cannot be empty. For this purpose, we should explain why $h$ crosses both $B_{\bm{t}}$ and $r'$. However, $h$ crossing $r$ implies $h$ crossing $r'$, as has already been argued in our proof of statement (2). It remains to show that $h$ crosses $B_\bm{t}$.

@@

\extraspacing {\bf Proof of Lemma~\ref{lmm:hv:type1:cross-r*}.} We will prove each statement in turn.

\extraspacing{\em Proof of Statement (1).} We will map each $r^*$ of $\bigcup_{i = 1}^{k-2} R_i^*$ to a unique tuple $\bm{t}$ in $\J(R_1',...,R_{k-2}')$ satisfying $\dcross_H(\bm{t})$ $= \cross_H(r^*)$. After this, we can then derive
\myeqn{
    \sum_{i\in[k-2]}\sum_{r^*\in R_i^*} |\cross_H(r^*)| \leq \sum_{\bm{t}\in \J(R_1',...,R_{k-2}')}|\dcross_H(\bm{t})|\leq \out \nn
}
where the last step used  statement (3) of Lemma~\ref{lmm:hv:type1:properties}.
